Surface-driven registration method for the structure-informed segmentation of diffusion MR images\tnoteref{t1}

### 2015-10-01 Publications/2015-NeuroImage/05-results.tex
fixed some numbers with text style

The results demonstrated that the accuracy was consistent and high, and below the image resolution.
\autoref{fig:phantom} (block C) shows the violin plots for each model type corresponding
  to the two sets of resolutions for the generated phantoms.
In order to relate the average misregistration error to the resolution of the moving image,
  we proceeded as follows.
First, we confirmed that the vertex-wise error distributions were skewed by using Shapiro-Wilk's test of
  normality.
All of the distributions of errors in the tests (four phantom types $\times$ two resolutions) were
  non-normal with $p<0.001$.
Consequently, we used the non-parametric Wilcoxon signed-rank test with the Bonferroni
  correction for multiple comparisons ($N=150$, for each phantom type).
The average errors were significantly lower than the voxel size with $p < (0.001 / 150)$
  in all tests (four phantom types $\times$ two resolutions).
Statistical tests might not be sufficiently conclusive, so we also computed the confidence intervals,
  as shown in \autoref{tab:ci_phantom}.

@@

\begin{table}
\centering
\footnotesize
\tabcolsep=0.1cm
\begin{minipage}{.48\textwidth}
    \vskip-4.7ex
    \begin{tabular}{lccccc}
    Res.   & ``gyrus'' & ``ball''  & ``box''   & ``L''     & Aggreg.    \\\hline
    1.0mm  & 0.18-0.38 & 0.31-0.45 & 0.34-0.42 & 0.34-0.40 & 0.34-0.38  \\
    2.0mm  & 0.59-0.60 & 0.65-0.76 & 0.68-0.71 & 0.67-0.77 & 0.64-0.66  \\
    \hline
    \end{tabular}
    \caption{The distributions of vertex-wise Hausdorff distances between the ground-truth surfaces and their
    corresponding estimates obtained with \regseg{} presented a 95\% CI below the half-voxel size for all of
    the phantom types.
    The CIs were computed by bootstrapping using 10$^4$ samples, with the median as the location statistic.}\label{tab:ci_phantom}
\end{minipage}
\hfill
\begin{minipage}{.48\textwidth}
    \begin{tabular}{cccccc}
    & & $\Gamma_{VdGM}$  & $\Gamma_{WM}$ & $\Gamma_{pial}$ & Aggreg. \\
    \hline
    \multirow{2}{*}{CI}
       & \regseg{} & 0.50--0.78 & 0.50--0.55 & 0.66--0.73 & 0.56--0.66 \\
       & T2B       & 1.78--2.58 & 1.94--2.36 & 2.16--2.58 & 2.05--2.39 \\
    \hline
    \multirow{2}{*}{H-tests}
       & p-value  & 4.1\e{-6} & 2.3\e{-6} & 2.3\e{-6} & 1.8\e{-16} \\
       & H-stat   & 21.20 & 22.31 & 22.31 & 67.85 \\
    \hline
    \end{tabular}
    \caption{Statistical analysis of results obtained using real data, which show that \regseg{} performed better than
    the alternative \acrfull{t2b} method.
    The distribution of the errors computed for the surfaces of interest ($\Gamma_{VdGM}$, $\Gamma_{WM}$, $\Gamma_{pial}$)
      and the aggregate of all surfaces (Aggreg. column) had lower 95\% CIs with \regseg{}.
   The CIs in this table were computed by bootstrapping using the mean as the location statistic and with 10$^4$ samples.
    The Kruskal-Wallis H-tests indicated that there was a significant difference between the results obtained using \regseg{} and
      the \gls*{t2b} method.
    }\label{tab:results_real}
\end{minipage}
\end{table}

>>>>

The results demonstrated that the accuracy was consistent and high, and below the image resolution.
\autoref{fig:phantom} (block C) shows the violin plots for each model type corresponding
  to the two sets of resolutions for the generated phantoms.
In order to relate the average misregistration error to the resolution of the moving image,
  we proceeded as follows.
First, we confirmed that the vertex-wise error distributions were skewed by using Shapiro-Wilk's test of
  normality.
All of the distributions of errors in the tests (four phantom types $\times$ two resolutions) were
  non-normal with $p<$ 0.001.
Consequently, we used the non-parametric Wilcoxon signed-rank test with the Bonferroni
  correction for multiple comparisons ($N$=150, for each phantom type).
The average errors were significantly lower than the voxel size with $p <$ (0.001 / 150)
  in all tests (four phantom types $\times$ two resolutions).
Statistical tests might not be sufficiently conclusive, so we also computed the confidence intervals,
  as shown in \autoref{tab:ci_phantom}.

@@

\begin{table}
\centering
\footnotesize
\tabcolsep=0.1cm
\begin{minipage}{.48\textwidth}
    \vskip-4.7ex
    \begin{tabular}{lccccc}
    Res.   & ``gyrus'' & ``ball''  & ``box''   & ``L''     & Aggreg.    \\\hline
    1.0mm  & 0.18-0.38 & 0.31-0.45 & 0.34-0.42 & 0.34-0.40 & 0.34-0.38  \\
    2.0mm  & 0.59-0.60 & 0.65-0.76 & 0.68-0.71 & 0.67-0.77 & 0.64-0.66  \\
    \hline
    \end{tabular}
    \caption{The distributions of vertex-wise Hausdorff distances between the ground-truth surfaces and their
    corresponding estimates obtained with \regseg{} presented a 95\% CI below the half-voxel size for all of
    the phantom types.
    The CIs were computed by bootstrapping using 10$^\text{4}$ samples, with the median as the location statistic.}\label{tab:ci_phantom}
\end{minipage}
\hfill
\begin{minipage}{.48\textwidth}
    \begin{tabular}{cccccc}
    & & $\Gamma_{VdGM}$  & $\Gamma_{WM}$ & $\Gamma_{pial}$ & Aggreg. \\
    \hline
    \multirow{2}{*}{CI}
       & \regseg{} & 0.50--0.78 & 0.50--0.55 & 0.66--0.73 & 0.56--0.66 \\
       & T2B       & 1.78--2.58 & 1.94--2.36 & 2.16--2.58 & 2.05--2.39 \\
    \hline
    \multirow{2}{*}{H-tests}
       & p-value  & 4.1\e{-6} & 2.3\e{-6} & 2.3\e{-6} & 1.8\e{-16} \\
       & H-stat   & 21.20 & 22.31 & 22.31 & 67.85 \\
    \hline
    \end{tabular}
    \caption{Statistical analysis of results obtained using real data, which show that \regseg{} performed better than
    the alternative \acrfull{t2b} method.
    The distribution of the errors computed for the surfaces of interest ($\Gamma_{VdGM}$, $\Gamma_{WM}$, $\Gamma_{pial}$)
      and the aggregate of all surfaces (Aggreg. column) had lower 95\% CIs with \regseg{}.
   The CIs in this table were computed by bootstrapping using the mean as the location statistic and with 10$^\text{4}$ samples.
    The Kruskal-Wallis H-tests indicated that there was a significant difference between the results obtained using \regseg{} and
      the \gls*{t2b} method.
    }\label{tab:results_real}
\end{minipage}
\end{table}

### 2015-10-01 Publications/2015-NeuroImage/06-discussion.tex
fixed some numbers with text style

We evaluated \regseg{} in a real environment using the experimental framework presented
  in \autoref{fig:evworkflows}.
We processed 16 subjects from the \gls*{hcp} database using both \regseg{}
  and an in-house replication of the \acrfull*{t2b} method.
\Regseg{} obtained very high accuracy, with an aggregate 95\% \gls*{ci} of 0.56--0.66 [mm], which was
  below the pixel size of 1.25 mm.
The misregistration error that remained after \regseg{} was significantly lower ($p < 0.01$) than the
  error corresponding to the \gls*{t2b} correction according to Kruskal-Wallis H-tests
  (\autoref{tab:results_real}).
Visual inspections of all the results (\suppl{section S5}) and the violin plots in
  \autoref{fig:results_real} confirmed that \regseg{} performed better than the \gls*{t2b} method
  in our settings.
We carefully configured the \gls*{t2b} method using the same algorithm and the
  same settings employed in a widely-used tool.
However, cross-comparison experiments are prone to so-called \emph{instrumentation bias}
  \citep{tustison_instrumentation_2013}.
Therefore, these results do not prove that \regseg{} \emph{is better than} \gls*{t2b}.
Our results suggest that \regseg{} is a reliable option in this application field.
In addition, the \gls*{t2b} may introduce an additional (and small) error during the necessary
  registration of \gls*{t2} in the \gls*{t1} space.

>>>>

We evaluated \regseg{} in a real environment using the experimental framework presented
  in \autoref{fig:evworkflows}.
We processed 16 subjects from the \gls*{hcp} database using both \regseg{}
  and an in-house replication of the \acrfull*{t2b} method.
\Regseg{} obtained very high accuracy, with an aggregate 95\% \gls*{ci} of 0.56--0.66 [mm], which was
  below the pixel size of 1.25 mm.
The misregistration error that remained after \regseg{} was significantly lower ($p <$ 0.01) than the
  error corresponding to the \gls*{t2b} correction according to Kruskal-Wallis H-tests
  (\autoref{tab:results_real}).
Visual inspections of all the results (\suppl{section S5}) and the violin plots in
  \autoref{fig:results_real} confirmed that \regseg{} performed better than the \gls*{t2b} method
  in our settings.
We carefully configured the \gls*{t2b} method using the same algorithm and the
  same settings employed in a widely-used tool.
However, cross-comparison experiments are prone to so-called \emph{instrumentation bias}
  \citep{tustison_instrumentation_2013}.
Therefore, these results do not prove that \regseg{} \emph{is better than} \gls*{t2b}.
Our results suggest that \regseg{} is a reliable option in this application field.
In addition, the \gls*{t2b} may introduce an additional (and small) error during the necessary
  registration of \gls*{t2} in the \gls*{t1} space.
